Javelins with hyper3 objects

### 2022-04-19 inst/javelin.Rmd
slight changes

@@

Inveestigation:

@@

@@

```{r,label=savejavelindataset}
save(javelin,javelin_table,javelin1_maxp,javelin2_maxp,  file="javelin.rda")
```

>>>>

We analyse results from the men's javelin, 2020 Summer Olympics.

@@

Investigation:

@@

Reference

@@

```{r,label=savejavelindataset}
save(javelin1,javelin2,javelin_table,javelin_vector,javelin1_maxp,javelin2_maxp,  file="javelin.rda")
```
